Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-23 paper/main.tex
added new paragraph to start of section 3

Across different versions of a given package, particular modules, functions,
and other objects may be updated, removed, renamed, or otherwise altered. In
addition to changing the behaviors of active computations, these changes can
render saved objects created using one version of a package incompatible with
other versions of the same package. For example, the popular
\texttt{pandas}~\cite{McKi10} library used to include the \texttt{Panel} data
structure for storing 3-dimensional arrays. Since version 0.20.0, however, the
\texttt{Panel} class has been deprecated, and in version 0.25.0, it was removed
entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
(created using an older version of \texttt{pandas}) and had saved it to their
disk (e.g., for later reuse or to share with other users) by serializing the
\texttt{Panel} with Python's \texttt{pickle} protocol. The \texttt{pickle}
protocol is a popular built-in method of persisting data in Python that allows
users to save, share, and load arbitrary objects. However, in order to
successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., previously saved)
object, the object's class must be defined in and importable from the same
module as when it was saved. Thus, because of the \texttt{Panel} class's
removal, the user's dataset could not be read by any version of \texttt{pandas}
from 0.25.0 or beyond. These incompatibilities are also not limited solely to
traditional forms of data. For example, saved model states and other objects
may reference modules, functions, attributes, classes, or other objects that
may not be identical (or even present) across all versions of their associated
package.

>>>>

%The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: a series of \texttt{smuggle} statements and onion comments with version specifiers or other options collectively define a
The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly. In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features and illustrate how they may be used to handle certain challenges that can arise with sharing reproducible scientific code.

Across different versions of a given package, various modules, functions,
and other objects may be updated, removed, renamed, or otherwise altered. In
addition to changing the behaviors of active computations, these changes can
render saved objects created using one version of a package incompatible with
other versions of the same package. For example, the popular
\texttt{pandas}~\cite{McKi10} library used to include the \texttt{Panel} data
structure for storing 3-dimensional arrays. Since version 0.20.0, however, the
\texttt{Panel} class has been deprecated, and in version 0.25.0, it was removed
entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
(created using an older version of \texttt{pandas}) and had saved it to their
disk (e.g., for later reuse or to share with other users) by serializing the
\texttt{Panel} with Python's \texttt{pickle} protocol. The \texttt{pickle}
protocol is a popular built-in method of persisting data in Python that allows
users to save, share, and load arbitrary objects. However, in order to
successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., previously saved)
object, the object's class must be defined in and importable from the same
module as when it was saved. Thus, because of the \texttt{Panel} class's
removal, the user's dataset could not be read by any version of \texttt{pandas}
from 0.25.0 or beyond. These incompatibilities are also not limited solely to
traditional forms of data. For example, saved model states and other objects
may reference modules, functions, attributes, classes, or other objects that
may not be identical (or even present) across all versions of their associated
package.
